An Efficient Minibatch Acceptance Test for Metropolis-Hastings

### 2017-02-05 icml2017/paper.tex
Fixed appendix a bit, added some of my table results.
This is for the deconvolution procedure. I think we should have more detailed tables, and then from looking at these systematically, we should find the good distribution to use and the target variance to use. I have an idea to have maybe six different sub-tables :) That's what the supplementary material is for

% Daniel: also need to modify table, add more info?
\begin{table}[t]
\caption{Error ($L_\infty$) in $X_{\rm norm}+X_{\rm corr}$ versus $X_{\rm log}$.}
\label{tab:xcorr}
\vskip 0.15in
\begin{center}
\begin{small}
\begin{sc}
\begin{tabular}{l l l l}
\hline
\abovespace\belowspace
${\bf N}$ & ${\bf \sigma}$ & ${\bf \lambda}$ & ${\bf L_{\infty}}$ {\bf error} \\
\hline
\abovespace
4000 & 0.9 & 1 & 1.0e-4  \\
\belowspace
4000 & 0.8 & 0.03 & 5.0e-6 \\
\hline
\end{tabular}
\end{sc}
\end{small}
\end{center}
\vskip -0.1in
\end{table}

With this approach, there is no guarantee that $u^* \geq 0$. However, we have
some flexibility in the choice of $\sigma$ in Equation~(\ref{eq:overall_corr_problem}).
As we decrease the variance of $X_{\rm norm}$, the variance of $X_{\rm corr}$
grows by the same amount and is in fact the result of convolution with a
Gaussian whose variance is the difference.  Thus as $\sigma$ decreases,
$C_\sigma(X)$ grows and approaches the derivative of a logistic function at
$\sigma = 0$. It retains some weak negative values for $\sigma > 0$ but removal
of those leads to small error. Table~\ref{tab:xcorr} shows that the errors
between $X_{\rm norm}+X_{\rm corr}$ and $X_{\rm log}$ approach single floating
precision (about $10^{-7}$), and Algorithm~\ref{alg:our_algorithm} describes our
procedure. A few points:

@@

Figure~\ref{fig:gauss_mix_1} shows scatter plots of the resulting $\theta$
samples for the three methods, with darker regions indicating a greater density
of points. There are no obvious differences, so we measure the similarity
between each set of samples and the actual posterior. \textbf{Daniel: I think
this was taking up too much space so I put it in Appendix~\ref{app:gaussians}.
Let's state the result (Table~\ref{tab:poissons}) and prioritize other stuff.
TODO}

@@

This appendix is divided into two main parts. Appendix~\ref{app:proofs} provides
the proofs that we omitted from the main text due to space constraints.
Appendix~\ref{app:experiments} provides further details on our experiments to
assist understanding and reproducibility.

@@

\section{Additional Experiment Details}\label{app:experiments}
% Daniel: all three experiments should be described in more detail here.

>>>>

With this approach, there is no guarantee that $u^* \geq 0$. However, we have
some flexibility in the choice of $\sigma$ in Equation~(\ref{eq:overall_corr_problem}).
As we decrease the variance of $X_{\rm norm}$, the variance of $X_{\rm corr}$
grows by the same amount and is in fact the result of convolution with a
Gaussian whose variance is the difference.  Thus as $\sigma$ decreases,
$C_\sigma(X)$ grows and approaches the derivative of a logistic function at
$\sigma = 0$. It retains some weak negative values for $\sigma > 0$ but removal
of those leads to small error. \textbf{Daniel: I moved this to
Appendix~\ref{app:correction} so that we can have more detailed results. For the
main text, let's state the value $\sigma$ and its error. Originally, we said:
Table~\ref{tab:xcorr} shows that the errors between $X_{\rm norm}+X_{\rm corr}$
and $X_{\rm log}$ approach single floating precision (about $10^{-7}$).}
Algorithm~\ref{alg:our_algorithm} describes our procedure. A few points:

@@

Figure~\ref{fig:gauss_mix_1} shows scatter plots of the resulting $\theta$
samples for the three methods, with darker regions indicating a greater density
of points. There are no obvious differences, so we measure the similarity
between each set of samples and the actual posterior. \textbf{Daniel: I think
this was taking up too much space so I put it in Appendix~\ref{app:gaussians}.
Let's state the result (in Table~\ref{tab:poissons}) and prioritize other stuff
here.  TODO}

@@

This appendix is divided into two main parts. Appendix~\ref{app:proofs} provides
the proofs that we omitted from the main text due to space constraints.
Appendix~\ref{app:experiments} provides further details on the correction
distribution derivation and on our three main experiments to assist
understanding and reproducibility.

@@

\section{Additional Experiment Details}\label{app:experiments}
% Daniel: all three experiments should be described in more detail here. And
% also the deconvolution step to get the correction distribution.

\subsection{Obtaining the Correction Distribution (Section~\ref{sec:correction})}\label{app:correction}

% Daniel: moved to appendix so we can expand it. Originally we had only two
% lines, and it looked pretty awkward. So let's add more. Note: this also
% depends on whether we use [-10,10] for the X_c range, or [-20,20], etc...
\begin{table}[t]
\caption{Error ($L_\infty$) in $X_{\rm norm}+X_{\rm corr}$ versus $X_{\rm log}$.}
\label{tab:xcorr}
\vskip 0.15in
\begin{center}
\begin{small}
\begin{sc}
\begin{tabular}{l l l l}
\hline
\abovespace\belowspace
${\bf N}$ & ${\bf \sigma}$ & ${\bf \lambda}$ & ${\bf L_{\infty}}$ {\bf error} \\
\hline
\abovespace
4000 & 1.0 & 100    & 1.9e-3  \\
4000 & 1.0 & 10     & 8.9e-4  \\
4000 & 1.0 & 1      & 1.6e-3  \\
4000 & 1.0 & 0.1    & 2.8e-3  \\
4000 & 1.0 & 0.01   & 5.2e-3  \\
4000 & 1.0 & 0.001  & 9.9e-3  \\
2000 & 1.0 & 10     & 1.3e-3  \\
8000 & 1.0 & 10     & 1.3e-3  \\
\belowspace
4000 & 1.0 & 10 & 6.6e-4 \\
\hline
\end{tabular}
\quad
\begin{tabular}{l l l l}
\hline
\abovespace\belowspace
${\bf N}$ & ${\bf \sigma}$ & ${\bf \lambda}$ & ${\bf L_{\infty}}$ {\bf error} \\
\hline
\abovespace
4000 & 0.9 & 1 & 1.0e-4  \\
\belowspace
4000 & 0.8 & 0.03 & 5.0e-6 \\
\hline
\end{tabular}
\end{sc}
\end{small}
\end{center}
\vskip -0.1in
\end{table}

\textbf{Daniel: TODO, figure out what values to test, put optimal values in bold
face here, etc., note that these are with the range $[-20,20]$ except for the
best value in $[-10,10]$; maybe we should decrease the range?}
